---
theme-settings:
  theme: yeti
  max-width: 2000px
  barposition: top
  footer-left: "Made with [surveydown](https://surveydown.org)"

survey-settings:
  mode: preview
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
  all-shuffled: false
  required:
    - consent
    - expectations
    - community_connection
    - field_belonging
    - partners_collaborators
    - professional_relationships
    - institutional_visibility
    - institutional_challenges
    - student_impacts
    - genomics_advocacy

system-messages:
  warning: Please answer the required questions before continuing.
  previous: Previous Page
  next: Next Page
  exit: Finish Survey
---

```{r echo = FALSE, message = FALSE}
library(surveydown)

likert_options <- c(
  "Not at all (1)"   = "1",
  "Slightly (2)"     = "2",
  "Moderately (3)"   = "3",
  "Quite a bit (4)"  = "4",
  "Very much (5)"    = "5"
)

knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

--- consentpage

# Instructions to Participants

Thank you for participating in the survey! We are collecting data about your experience as members of this community. This data will be used for reporting to the NIH and may be shared with similar communities.

### Data confidentiality

Responses are anonymous. The potential risks to you are small. The potential benefits to the education community are high—we will use this information to report on the successes and challenges associated with the AI-GENe Program. Please do not include names, institution names, email addresses, or other identifying information in your written responses.

### Data sharing

No personally identifiable information, such as response timestamps, will be shared.

### Participation

You must be 18 or over to participate. You will be asked a series of questions about participating in the AI-GENe Program. **By completing this survey or questionnaire, you are consenting to be in this research study. Your participation is voluntary, and you can stop at any time.** You do not need to answer optional questions. Any answers you have filled in will be automatically submitted if you close the browser tab.

Depending on how you answer the survey, this will take about **5 minutes** to complete.

### Risk

Risk of participation is minimal. The questions we ask pose minimal security risk to participants, as they focus on your personal experience and expectations. While we have taken measures to ensure the security of the survey responses, please be aware that no online system is completely secure. By participating in this survey, you understand and accept the inherent risks associated with transmitting information over the internet.

### Consent

The first question asks whether you are at least 18 years old and whether you consent, or agree, that data from your responses may be used for AI-GENe reporting purposes.

<br>

## Questions or problems

If you have questions or problems, contact:

- Ava Hoffman at [ahoffma2@fredhutch.org](mailto:ahoffma2@fredhutch.org)
- Michael Schatz at [mschatz@jhu.edu](mailto:mschatz@jhu.edu)

You may also contact the Johns Hopkins University Homewood Institutional Review Board (IRB) if you have questions about your rights as a participant. Contact the IRB if you feel you have not been treated fairly or if you have other concerns.

- **IRB No.:** HIRB00024197
- **Date approved:** XX/XX/2026
- **HIRB Office phone:** 410-516-6580
- **HIRB Office email:** [hirb@jhu.edu](mailto:hirb@jhu.edu)

<br>

## Consent for answers to be used by AI-GENe staff

```{r}
sd_question(
  type = "mc",
  id = "consent",
  label = paste(
    "I am 18 or over *AND* I consent to my responses being used",
    "for AI-GENe evaluation and reporting purposes."
  ),
  option = c(
    "Yes" = "yes",
    "No"  = "no"
  )
)
```

--- page2

# Professional development

The following questions ask about the impact AI-GENe had on your professional development.

```{r}
sd_question(
  type = "mc",
  id = "expectations",
  label = "AI-GENe has met or exceeded my initial expectations.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "community_connection",
  label = paste(
    "AI-GENe made me feel more connected to the broader genomics",
    "research and education community."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "field_belonging",
  label = paste(
    "My involvement in AI-GENe has strengthened my sense of belonging",
    "in the genomics field."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "partners_collaborators",
  label = paste(
    "I consider NHGRI partners and AI-GENe organizers",
    "(e.g., Johns Hopkins) to be collaborators."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "professional_relationships",
  label = paste(
    "AI-GENe activities (virtual meetings, working groups, and",
    "in-person meetings) helped me build professional relationships."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "institutional_visibility",
  label = paste(
    "AI-GENe activities have increased my visibility as a leader in",
    "genomics and/or data science at my institution."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "institutional_challenges",
  label = paste(
    "AI-GENe helped me address the unique challenges I face",
    "at my institution."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "work_connections",
  label = paste(
    "Optional: AI-GENe connections have been a core part of my",
    "recent work/research."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "textarea",
  id = "professional_comments",
  label = "Optional: In a few sentences, tell us about your responses above."
)
```

--- page3

# Teaching and students

The following questions ask about the impact AI-GENe had on your teaching and students.

```{r}
sd_question(
  type = "mc",
  id = "student_impacts",
  label = paste(
    "I can identify positive impacts of AI-GENe and/or BioDIGS on my",
    "students' academic and career trajectories."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "genomics_advocacy",
  label = paste(
    "AI-GENe has helped me effectively advocate for genomics education",
    "at my institution."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "teaching_ability",
  label = paste(
    "Optional: AI-GENe participation has increased my ability to teach",
    "genomic data science concepts."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "textarea",
  id = "teaching_comments",
  label = "Optional: In a few sentences, tell us about your responses above."
)
```

--- page4

# Your experience with AI-GENe

The following open-ended questions are **optional**.

Please do not include names, institution names, email addresses, or other identifying information in your responses.

```{r}
sd_question(
  type = "textarea",
  id = "memorable_experience",
  label = "What is your most memorable experience from AI-GENe?"
)
```

```{r}
sd_question(
  type = "textarea",
  id = "future_improvements",
  label = "How would you improve a future AI-GENe?"
)
```

```{r}
sd_question(
  type = "textarea",
  id = "helpful_activities",
  label = "What activities did you find most helpful?"
)
```

```{r}
sd_question(
  type = "textarea",
  id = "helpful_materials",
  label = "What materials did you find most helpful?"
)
```

```{r}
sd_question(
  type = "textarea",
  id = "valuable_outcome",
  label = paste(
    "What has been the single most valuable outcome of your",
    "AI-GENe participation?"
  )
)
```

```{r}
sd_question(
  type = "textarea",
  id = "other_feedback",
  label = paste(
    "Please share any other thoughts or feedback you have related",
    "to AI-GENe."
  )
)
```

--- end

Thank you for completing the AI-GENe survey.

Select **Finish Survey** below to submit your responses.

```{r}
sd_close()
```

--- ineligible

Thank you for your interest. You must be at least 18 years old and consent to the use of your responses for AI-GENe evaluation and reporting purposes to participate in this survey.

Select **Finish Survey** below to close the survey.

```{r}
sd_close()
```