---
title: Faculty Pre Post Retrospective

theme-settings:
  theme: yeti
  barposition: top
  footer-left: "Made with [surveydown](https://surveydown.org)"

survey-settings:
  mode: preview
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
  all-shuffled: false
  required:
    - consent
    - institution_type
    - teaching_confidence
    - community_of_practice
    - classroom_barriers
    - real_world_significance
    - student_genomics_interest
    - student_research_interest
    - mentor_advanced_students
    - train_other_instructors
    - incorporate_similar_content

system-messages:
  warning: Please answer the required questions before continuing.
  previous: Previous Page
  next: Next Page
  exit: Finish Survey
---

```{r echo=FALSE, message=FALSE}
library(surveydown)

likert_options <- c(
  "Not at all (1)"  = "1",
  "Slightly (2)"    = "2",
  "Moderately (3)"  = "3",
  "Quite a bit (4)" = "4",
  "Very much (5)"   = "5"
)

institution_options <- c(
  'Doctoral University - Very high research activity ("R1")' = "r1",
  'Doctoral University - High research activity ("R2")'      = "r2",
  "Master's College or University"                           = "masters",
  "Primarily Undergraduate Institution (PUI)"                = "pui",
  "Community College"                                        = "community_college",
  "High School"                                              = "high_school",
  "Other"                                                    = "other"
)

knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# Create nice html and pdf
# pagedown::chrome_print("survey.qmd", "01_Faculty_Pre_Post_Retrospective.pdf")
# Create simple word doc
# pandoc survey.html -o 01_Faculty_Pre_Post_Retrospective.docx
```

--- consentpage

# Instructions to Participants

Thank you for participating in the survey! We are collecting data about your experience leading or teaching the AI-GENe modules. This data will be used to guide the AI-GENe Program and may ultimately be used for a research publication and reporting to the NIH.

### Data confidentiality

Responses are anonymous. The potential risks to you are small. The potential benefits to the education community are high—we will use this information to guide the development of educational material. Please do not include names, institution names, email addresses, or other identifying information in your written responses.

### Data sharing

No personally identifiable information, such as response timestamps, will be shared.

### Participation

You must be 18 or over to participate. You will be asked a series of questions about your experience with the AI-GENe modules. **By completing this survey or questionnaire, you are consenting to be in this research study. Your participation is voluntary, and you can stop at any time.** You do not need to answer optional questions. Any answers you have filled in will be automatically submitted if you close the browser tab.

Depending on how you answer the survey, this will take about **3 minutes** to complete.

### Risk

Risk of participation is minimal. The questions we ask pose minimal security risk to participants, as they focus on your personal experience and expectations. While we have taken measures to ensure the security of the survey responses, please be aware that no online system is completely secure. By participating in this survey, you understand and accept the inherent risks associated with transmitting information over the internet.

### Consent

The first question asks whether you are at least 18 years old and whether you consent, or agree, that data from your responses may be used for AI-GENe development purposes.

<br>

## Questions or problems

If you have questions or problems, contact:

- Ava Hoffman at [ahoffma2@fredhutch.org](mailto:ahoffma2@fredhutch.org)
- Michael Schatz at [mschatz@jhu.edu](mailto:mschatz@jhu.edu)

You may also contact the Johns Hopkins University Homewood Institutional Review Board (IRB) if you have questions about your rights as a participant. Contact the IRB if you feel you have not been treated fairly or if you have other concerns.

- **IRB No.:** HIRB00024197
- **Date approved:** XX/XX/2026
- **HIRB Office phone:** 410-516-6580
- **HIRB Office email:** [hirb@jhu.edu](mailto:hirb@jhu.edu)

<br>

## Consent for answers to be used by AI-GENe staff

```{r}
sd_question(
  type = "mc",
  id = "consent",
  label = paste(
    "I am 18 or over *AND* I consent to my responses being used",
    "for AI-GENe evaluation and development."
  ),
  option = c(
    "Yes" = "yes",
    "No"  = "no"
  )
)
```

<br>

--- institution

# About your institution

```{r}
sd_question(
  type = "mc",
  id = "institution_type",
  label = "Describe the institution where you do most of your instruction.",
  option = institution_options
)
```

```{r}
sd_question(
  type = "textarea",
  id = "institution_other",
  label = paste(
    'If you selected "Other," please provide a description of the type',
    "of institution where you do most of your instruction."
  )
)
```

<br>

--- experience1

# Experience leading or teaching AI-GENe modules

These questions are intended to help you reflect on your experience leading or teaching AI-GENe modules. Please rate how much you agree with each statement.

```{r}
sd_question(
  type = "mc",
  id = "teaching_confidence",
  label = paste(
    "My confidence has improved after leading or teaching",
    "the AI-GENe module."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "community_of_practice",
  label = paste(
    "Leading or teaching the AI-GENe module contributed to my",
    "sense of community of practice."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "classroom_barriers",
  label = paste(
    "I experienced barriers bringing the AI-GENe module",
    "into the classroom."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "real_world_significance",
  label = "The AI-GENe module had real-world significance.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "student_genomics_interest",
  label = paste(
    "My students have shown greater interest in genomics",
    "following the AI-GENe module."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "student_research_interest",
  label = paste(
    "My students have shown greater interest in research or education",
    "following the AI-GENe module."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "mentor_advanced_students",
  label = "I plan to mentor advanced students.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "train_other_instructors",
  label = "I plan to mentor or train other instructors.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "incorporate_similar_content",
  label = paste(
    "I plan to incorporate more content similar to",
    "the AI-GENe module."
  ),
  option = likert_options
)
```

```{r}
sd_question(
  type = "textarea",
  id = "response_elaboration",
  label = "Please elaborate on any of your responses above."
)
```

<br>

--- end

Thank you for completing the AI-GENe survey.

Select **Finish Survey** below to submit your responses.

```{r}
sd_close()
```

<br>

--- ineligible

Thank you for your interest. You must be at least 18 years old and consent to the use of your responses for AI-GENe evaluation and reporting purposes to participate in this survey.

Select **Finish Survey** below to close the survey.

```{r}
sd_close()
```