---
title: AI-GENe Long-Term Follow-Up Survey

theme-settings:
  theme: yeti
  barposition: top
  footer-left: "Made with [surveydown](https://surveydown.org)"
  footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/fhdsl/AI-GENe_surveys)'

survey-settings:
  mode: preview
  show-previous: true
  use-cookies: false
  auto-scroll: false
  rate-survey: false
  system-language: en
  highlight-unanswered: true
  highlight-color: blue
  capture-metadata: true
  all-required: false
  all-shuffled: false
  required:
    - consent
    - institution_type
    - activities
    - modules_implemented
    - classroom_barriers
    - real_world_significance
    - student_genomics_interest
    - student_research_interest
    - incorporated_similar_content_classroom
    - students_reached
    - confidence_improved
    - community_of_practice
    - mentored_advanced_students
    - trained_instructors
    - incorporated_similar_content_program

system-messages:
  warning: Please answer the required questions before continuing.
  previous: Previous Page
  next: Next Page
---

```{r echo = FALSE, message = FALSE}
library(surveydown)

likert_options <- c(
  "Not at all (1)"  = "1",
  "Slightly (2)"    = "2",
  "Moderately (3)"  = "3",
  "Quite a bit (4)" = "4",
  "Very much (5)"   = "5"
)

institution_options <- c(
  'Doctoral University - Very high research activity ("R1")' =
    "doctoral_r1",
  'Doctoral University - High research activity ("R2")' =
    "doctoral_r2",
  "Master's College or University" =
    "masters_college_university",
  "Primarily Undergraduate Institution (PUI)" =
    "primarily_undergraduate",
  "Community College" =
    "community_college",
  "High School" =
    "high_school",
  "Other" =
    "other"
)

activity_options <- c(
  "Attended a train-the-trainer workshop" =
    "train_the_trainer",
  "Implemented AI-GENe modules in the classroom" =
    "classroom",
  "Attended online events hosted by the AI-GENe training academy" =
    "online_events",
  "Other" =
    "other"
)

module_options <- c(
  "Genome Annotation and the Phenotypic Effects of Variants" =
    "genome_annotation_variants",
  "Predicting Gene Expression Patterns" =
    "gene_expression",
  "Predicting Protein Structure from Genomic Data" =
    "protein_structure",
  "Sample Collection and HMW DNA Isolation" =
    "sample_collection_hmw_dna",
  "Assessing and Improving DNA Quality" =
    "dna_quality",
  "DNA Library Preparation and Long Read Sequencing" =
    "library_preparation_long_read",
  "Sequencing Data QC & Taxonomic Profiling" =
    "sequencing_qc_taxonomic_profiling",
  "Metagenome Assembly & AMR Gene Annotation" =
    "metagenome_assembly_amr",
  "LLMs and Scientific Literacy" =
    "llms_scientific_literacy",
  "Full miniCURE (all modules listed above)" =
    "full_minicure",
  "Other" = "other"
)

students_reached_options <- c(
  "1–10"    = "1_10",
  "11–40"   = "11_40",
  "41–80"   = "41_80",
  "81–150"  = "81_150",
  "151–300" = "151_300",
  "Over 300" = "over_300"
)

knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r eval = FALSE}
# Render print versions
pagedown::chrome_print("survey.qmd", "06_Faculty_Long_Term.pdf")
system("pandoc survey.html -o 06_Faculty_Long_Term.docx")
```

--- consentpage

# Instructions to Participants

Thank you for participating in the survey! We are collecting data about your long-term experience with the AI-GENe Program. This data will be used to guide the AI-GENe Program and may ultimately be used for a research publication and reporting to the NIH.

### Data confidentiality

Responses are anonymous. The potential risks to you are small. The potential benefits to the education community are high—we will use this information to guide development of education material. Please do not include names, institution names, email addresses, or other identifying information in your written responses.

### Data sharing

No personally identifiable information, such as response timestamps, will be shared.

### Participation

You must be 18 or over to participate. You will be asked a series of questions about your experience with the AI-GENe modules. **By completing this survey or questionnaire, you are consenting to be in this research study. Your participation is voluntary, and you can stop at any time.** You do not need to answer optional questions. Any answers you have filled in will be automatically submitted if you close the browser tab.

Depending on how you answer the survey, this will take about **3–6 minutes** to complete.

### Risk

Risk of participation is minimal. The questions we ask pose minimal security risk to participants, as they focus on your personal experience and expectations. While we have taken measures to ensure the security of the survey responses, please be aware that no online system is completely secure. By participating in this survey, you understand and accept the inherent risks associated with transmitting information over the internet.

### Consent

The first question asks whether you are at least 18 years old and whether you consent, or agree, that data from your responses may be used for AI-GENe development purposes.

<br>

## Questions or problems

If you have questions or problems, contact:

- Ava Hoffman at [ahoffma2@fredhutch.org](mailto:ahoffma2@fredhutch.org)
- Michael Schatz at [mschatz@jhu.edu](mailto:mschatz@jhu.edu)

You may also contact the Johns Hopkins University Homewood Institutional Review Board (IRB) if you have questions about your rights as a participant. Contact the IRB if you feel you have not been treated fairly or if you have other concerns.

- **IRB No.:** HIRB00024197
- **Date approved:** XX/XX/2026
- **HIRB Office phone:** 410-516-6580
- **HIRB Office email:** [hirb@jhu.edu](mailto:hirb@jhu.edu)

<br>

## Consent for answers to be used by AI-GENe staff

```{r}
sd_question(
  type = "mc",
  id = "consent",
  label = "I am 18 or over AND I consent to my responses being used for AI-GENe evaluation and development.",
  option = c(
    "Yes" = "yes",
    "No"  = "no"
  )
)
```

<br>

--- background

# About you and your participation

```{r}
sd_question(
  type = "mc",
  id = "institution_type",
  label = "Describe the institution where you do most of your instruction.",
  option = institution_options
)
```

```{r}
sd_question(
  type = "textarea",
  id = "institution_other",
  label = "(Optional) If you selected “Other,” please provide a description of the type of institution where you do most of your instruction."
)
```

```{r}
sd_question(
  type = "mc_multiple",
  id = "activities",
  label = "What activities did you do associated with the AI-GENe project? Please check all that apply.",
  option = activity_options
)
```

```{r}
sd_question(
  type = "textarea",
  id = "activities_other",
  label = "(Optional) If you selected “Other,” please elaborate."
)
```

<br>

--- implementation

# Reflecting on classroom implementation

These questions are intended to help you reflect on the long-term impacts of implementing AI-GENe materials in your classroom.

```{r}
sd_question(
  type = "mc_multiple",
  id = "modules_implemented",
  label = "Which modules did you implement? Please check all that apply.",
  option = module_options
)
```

<br>

## Classroom experience

Please rate how much you agree with the following statements.

```{r}
sd_question(
  type = "mc",
  id = "classroom_barriers",
  label = "I experienced barriers bringing the AI-GENe module(s) into the classroom.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "real_world_significance",
  label = "The AI-GENe material has real-world significance.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "student_genomics_interest",
  label = "My students have shown greater interest in genomics following the AI-GENe material.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "student_research_interest",
  label = "My students have shown greater interest in research or education following the AI-GENe material.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "incorporated_similar_content_classroom",
  label = "I have incorporated more content similar to the AI-GENe module.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "students_reached",
  label = "How many students do you estimate you reached with AI-GENe materials?",
  option = students_reached_options
)
```


<br>

Please do not include names, institution names, email addresses, or other identifying information in your responses.

```{r}
sd_question(
  type = "textarea",
  id = "classroom_elaboration",
  label = "Please elaborate on any of your responses above."
)
```

```{r}
sd_question(
  type = "textarea",
  id = "material_changes",
  label = "Did you make any changes to the material? If so, please describe."
)
```

<br>

--- longterm

# Long-term program impacts

These questions are intended to help you reflect on the long-term impacts of your participation with the AI-GENe Program.

Please rate how much you agree with the following statements.

```{r}
sd_question(
  type = "mc",
  id = "confidence_improved",
  label = "My confidence has improved after participating in the AI-GENe Program.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "community_of_practice",
  label = "The AI-GENe Program contributed to my sense of community of practice.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "mentored_advanced_students",
  label = "I have mentored advanced students.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "trained_instructors",
  label = "I have mentored or trained other instructors.",
  option = likert_options
)
```

```{r}
sd_question(
  type = "mc",
  id = "incorporated_similar_content_program",
  label = "I have incorporated more content similar to the AI-GENe module.",
  option = likert_options
)
```

<br>

Please do not include names, institution names, email addresses, or other identifying information in your responses.

```{r}
sd_question(
  type = "textarea",
  id = "program_elaboration",
  label = "Please elaborate on any of your responses above."
)
```

```{r}
sd_question(
  type = "textarea",
  id = "professional_success",
  label = "Did AI-GENe contribute to a proposal, presentation, publication, course, new educational activity, or any other professional development success in your career? If so, please describe."
)
```

<br>

--- end

Thank you for completing the AI-GENe survey.

Click **Exit Survey** below to finish.

```{r}
sd_close()
```

<br>

--- ineligible

Thank you for your interest. You must be at least 18 years old and consent to the use of your responses for AI-GENe evaluation and reporting purposes to participate in this survey.

Click **Exit Survey** below to finish.

```{r}
sd_close()
```